Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-04 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

LD generators are the most prevalent generally available components of QMC software.  These generators appear in Association of Computing Machinery  publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, libseq \cite{FriKel02,FriKelweb}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, MATLAB \cite{MAT9.13}, SamplePack \cite{SamplePack}, Gr\"nschlo{\ss}'s website \cite{GruWeb}, the Magic Point Shop \cite{NuyWeb}, R \cite{QRNG2020}, Julia \cite{QMCJulia}, SciPy \cite{virtanen2020scipy}, PyTorch \cite{paszke2019pytorch}, and TensorFlow \cite{tfqfQMC2021a}, and MatBuilder \cite{paulin2022}.

@@

For the comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, including the LD sequence generators allow users to a ????

@@

 Joe and Kuo

Finally, a \emph{stopping criterion} is determines the sample size, $n$, required to satisfy the error criterion \eqref{CDHS_eq:error_tol} given in terms of the absolute error tolerance, $\varepsilon$.  One can also imagine error criteria involving a relative error tolerance or a combination of absolute and relative error tolerances.

No one software library contains all of these features, which is why great QMC software must be well integrated into other software libraries.  This may mean large libraries including QMC routines and/or building connections between QMC libraries and other libraries.

>>>>

LD generators are the most prevalent generally available components of QMC software.  These generators appear in Association of Computing Machinery  publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, libseq \cite{FriKel02,FriKelweb}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, MATLAB \cite{MAT9.13}, SamplePack \cite{SamplePack}, Gr\"unschlo{\ss}'s website \cite{GruWeb}, the Magic Point Shop \cite{NuyWeb}, R \cite{QRNG2020}, Julia \cite{QMCJulia}, SciPy \cite{virtanen2020scipy}, PyTorch \cite{paszke2019pytorch}, and TensorFlow \cite{tfqfQMC2021a}, MatBuilder \cite{paulin2022}, and  QMCPy \cite{QMCPy2020a}.

@@

For the comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, the LD sequence generators included already allow users to easily access them while drawing from other packages in these environments.  However, the developers of smaller libraries, like BRODA and QMCPy should assume the responsibility of showing how their libraries can connect well with others.

@@

Complex integrands might be best evaluated by libraries that have no direct connection to QMC software libraries.  In the uncertainty quantification (UQ) space, the recently developed UM-Bridge \cite{umbridge} (the UQ and Model Bridge), which connects libraries that generate sequences of model parameters, $\bsx_1, \bsx_2, \ldots$ with libraries that evaluate models, $f(\bsx_1), f(\bsx_2), \ldots$.  We illustrate how UM-Bridge connects QMCPy with a differential equation solver for a cantilevered beam with random Young's modulus \cite{ParSee22a}.

\begin{figure}
    \centering
    \includegraphics[width=0.3\textwidth]{cantileveredbeam.eps}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

\subsection{Stopping Criteria}
Finally, a \emph{stopping criterion} is determines the sample size, $n$, required to satisfy the error criterion \eqref{CDHS_eq:error_tol} given in terms of the absolute error tolerance, $\varepsilon$.  One can also imagine error criteria involving a relative error tolerance or a combination of absolute and relative error tolerances.

\subsection{??}
No one software library contains all of these features, which is why great QMC software must be well integrated into other software libraries.  This may mean large libraries including QMC routines and/or building connections between QMC libraries and other libraries.
